Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-24 paper.tex
Edits to section on assumptions

\subsection{Assumptions}
In this secion, we discuss several assumptions that we need to acheive our results.  Denote

\begin{align}
\Omega_{i,j}=\{\theta:B(\theta)=i, \hat{B}(\theta)=j\}, \nonumber 
\end{align}
which is the users whose best arm is arm $i$ and the second best arm is arm $j$. We need the following assumptions in our analysis:

@@

Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm. For simplicity in our analysis, we use a slightly stronger condition below: $M=\max_{i,j}sup_{y\in R^{+}}f_{i,j}(y) <\infty$.

@@

Throughout this write up, we use $R$ to denote the maximum regret it can occur at each time. We know $R<\infty$ due to Assumption~\ref{A2}.

@@

Assumption~\ref{A3} means for each arm $i$, there exist a positive proportion of users whose best arm is $i$.

>>>>

\subsection{Assumptions}
In this secion, we state several assumptions assumed by our analysis.  First define
\begin{align}
\Omega_{i,j}=\{\theta:B(\theta)=i, \hat{B}(\theta)=j\}, \nonumber 
\end{align}
which is the set of agent preferences whose best arm is arm $i$ and second best arm is arm $j$. With this definition, our analysis makes the following assumptions:

@@

Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm. For simplicity in our analysis, we use a slightly stronger condition below: $M=\max_{i,j}sup_{y\in R^{+}}f_{i,j}(y) <\infty$.  \pfcomment{Let's state the assumption in terms of $M$, which is what our proof uses, and then if you want to say that we can also show similar results for $M'$ we can say that informally here.}

@@

We use $R = \max_{\theta, i,j} \theta \cdot (u_i - u_j)$ to denote the maximum regret that can be incurred at each time.  Assumption~\ref{A2} shows that $R<\infty$.

@@

Assumption~\ref{A3} means each arm $i$ has a strictly positive proportion of users for which that arm is best.
